---
title: "p8105_hw5_co2616"
output: github_document
date: "2025-11-14"
---

```{r}
library(tidyverse)
library(broom)
```

## Problem 1
 
creating a function where, for a fixed group size, randomly draws “birthdays” for each person; checks whether there are duplicate birthdays in the group; and returns TRUE or FALSE based on the result.
```{r}
bday_sim = function (n_room) {
  
  birthdays = sample(1:365, n_room, replace = TRUE)

  repeated_bday = length(unique(birthdays)) < n_room

  repeated_bday
}
```

running this function 10000 times for each group size between 2 and 50 and computing the average

```{r}
bday_sim_results = 
  expand_grid(
    room_size = 2:50,
  iter = 1:1000
  ) %>% 
  mutate(
    results = map_lgl(room_size, bday_sim)
  ) %>% 
  group_by(
    room_size
  ) %>% 
  summarise(
    prob_repeat = mean(results)
  )
```

plotting results
```{r}
bday_sim_results %>% 
  ggplot(aes(x = room_size, y = prob_repeat)) +
  geom_point() +
  geom_line()
```

As number of people in a room increases, there is a greater probability that at least two people share a birthday. In a room full of about 25 people, there would be a 50% chance that at least two people share a birthday. n a room full of about 50 people, there would be a 99% chance that at least two people share a birthday. 

## Problem 2

```{r}
null_df = function(n = 30, mu = 0, sigma = 5) {
  
 sim_df =
  tibble(
    x = rnorm(n = n, mean = mu, sd = sigma)
    )
 
 sim_df %>% 
    summarize(
       estimate = tidy(t.test(x))$estimate,
       p_val = tidy(t.test(x))$p.value
    ) 

}

```

```{r}
sim_results_df = 
  expand_grid(
    sample_size = 30,
    iter = 1:5000
  ) |> 
  mutate(
    estimate_df = map(sample_size, null_df)
  ) |> 
  unnest(estimate_df)

sim_results_df
```

```{r}
new_null_df = function(n = 30, mu = 0, sigma = 5) {
  
 new_sim_df =
  tibble(
    x = rnorm(n = n, mean = mu, sd = sigma)
    )
 
 new_sim_df %>% 
    summarize(
       new_estimate = tidy(t.test(x))$estimate,
       new_p_val = tidy(t.test(x))$p.value
    ) 

}
```

**Repeat the above for 𝜇={1,2,3,4,5,6}, and complete the following:**

```{r}
new_sim_results_df = 
  expand_grid(
    sample_size = 30,
    new_mu = c(1,2,3,4,5,6),
    iter = 1:5000
  ) |> 
  mutate(
    new_estimate_df = map2(sample_size, new_mu, new_null_df)
  ) |> 
  unnest(new_estimate_df)

new_sim_results_df
```

```{r}
new_sim_results_df %>%
  group_by(new_mu) %>%
  summarize(
    power = mean(new_p_val < 0.05)
  ) %>% 
  ggplot(aes(x = new_mu, y = power)) +
  geom_line()
```

As effect size increases, the power increases and when the true mean is 4, you have reached max power. 

```{r}
new_sim_results_df %>%
  group_by(new_mu) %>%
  filter(new_p_val < 0.05) %>% 
  summarize(
    avg_estimate = mean(new_estimate)
  ) %>% 
  ggplot(aes(x = new_mu, y = avg_estimate)) +
  geom_line()
```

Yes, the sample average of 𝜇̂ across tests for which the null is rejected approximately equal to the true value of 𝜇 because
