---
title: "p8105_hw5_co2616"
output: github_document
date: "2025-11-14"
---

```{r}
library(tidyverse)
```

## Problem 1
 
creating a function where, for a fixed group size, randomly draws “birthdays” for each person; checks whether there are duplicate birthdays in the group; and returns TRUE or FALSE based on the result.
```{r}
bday_sim = function (n_room) {
  
  birthdays = sample(1:365, n_room, replace = TRUE)

  repeated_bday = length(unique(birthdays)) < n_room

  repeated_bday
}
```

running this function 10000 times for each group size between 2 and 50 and computing the average

```{r}
bday_sim_results = 
  expand_grid(
    room_size = 2:50,
  iter = 1:1000
  ) %>% 
  mutate(
    results = map_lgl(room_size, bday_sim)
  ) %>% 
  group_by(
    room_size
  ) %>% 
  summarise(
    prob_repeat = mean(results)
  )
```

plotting results
```{r}
bday_sim_results %>% 
  ggplot(aes(x = room_size, y = prob_repeat)) +
  geom_point() +
  geom_line()
```

As number of people in a room increases, there is a greater probability that at least two people share a birthday. In a room full of about 25 people, there would be a 50% chance that at least two people share a birthday. n a room full of about 50 people, there would be a 99% chance that at least two people share a birthday. 

## Problem 2

